\documentclass[margin,line]{res}

\setlength{\parskip}{1.5pt} % 1ex plus 0.5ex minus 0.2ex}

\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 
\usepackage{hyperref}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{\textbf{Kushal K Dey} \vspace*{.1in}}


\begin{resume}
\section{\sc \textcolor{Orange}{Contact Information}}
\vspace{.05in}
\begin{tabular}{@{}p{0.5in}p{4in}}
Address: & 5220 S Kenwood Ave\\
               & Apt 108, Chicago IL, 60615  \\ [2 pt]
Email:     & \href{kkdey@uchicago.edu}{kkdey@uchicago.edu} , 
		\href{kdey@galton.uchicago.edu}{kdey@galton.uchicago.edu} \\ [3 pt]
             
Tel:         & +1-3127090680\\ [2 pt]
Sex:       &  Male \\ [2 pt]
DOB:      & 17$^{th}$ July,1989 \\
Website:  & \url{https://kkdey.github.io} \\
Twitter: &  \url{https://twitter.com/kanishkadey}

\end{tabular}


\section{\sc \textcolor{Orange}{Research Interests}}

I am primarily interested in applying Statistics and Machine Learning models to find structure in biological data. Recently, I have been working on applying admixture or topic model type algorithms to learn structure in data coming from RNA-seq, ecological applications and ancient DNA. In addition, I have been involved in building nonparametric methods to learn cell differentiation trees and cell cycle ordering from single cell RNA-seq data.

\section{\sc \textcolor{Orange}{Education}}
{\bf University of Chicago}, Chicago, IL, United States\\
\vspace*{-.1in}
\begin{list1}
\item[] \emph{PhD}, Statistics (expected graduation date: June 2018)
\item[] Advisor: Matthew Stephens, \textit{Stephens Lab}
\end{list1} 

\vspace{0.2in}

{\bf Indian Statistical Institute}, Kolkata, West Bengal, India\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] \emph{B.Stat, M.Stat}, Statistics (2008-2013)
\end{list1}


\section{\sc \textcolor{Orange}{Publications}}

\begin{enumerate}

\small{

\item \textbf{KK Dey}, C Hsiao, and M Stephens. Clustering RNA-seq expression data using grade of membership model. (http://biorxiv.org/content/early/2016/05/03/051631). \textit{under revision}

\item \textbf{KK Dey}, C Hsiao, and M Stephens. CountClust: Clustering and Visualizing RNA-Seq Expression Data using Grade of Membership Models. R package version 1.0.2, \\
(https://github.com/kkdey/CountClust).

\item AL Tarca, M Lauria, M Unger, E Bilal, S Boue, \textbf{KK Dey}, J Hoeng et al. Strengths and limitations of microarray-based phenotype prediction: lessons learned from the IMPROVER Diagnostic Signature Challenge. \textit{Bioinformatics}. 29 (22), pp 2892-2899. 2013.

\item P Nandy, M Unger, C Zechner, \textbf{KK Dey}, H Koeppl. Learning diagnostic signatures from microarray data using L1-regularized logistic regression. \textit{Systems Biomedicine}. 1 (4), 2013. 

\item A Das, S Adam, \textbf{KK Dey}, A Maiti. Hematopoietic stem cell transplantation in thalassemia: a systematic review of literature and meta analysis of prospective controlled trials. Submitted.

\item \textbf{KK Dey}, S Bhattacharya . On Optimal Scaling of Additive Transformation Based Markov Chain Monte Carlo Under Non-Regular Cases. Submitted to \textit{Bernoulli}. \\
(http://arxiv.org/abs/1405.0913)

\item \textbf{KK Dey}, S Bhattacharya. On Optimal Scaling of Additive Transformation Based Markov Chain Monte Carlo.  \textit{Brazilian Journal of Probability and Statistics}. Accepted.\\
(http://arxiv.org/pdf/1307.1446v4.pdf)

\item B Karmakar, K Dhara, \textbf{KK Dey}, A Basu, AK Ghosh. Tests for statistical significance of a treatment effect in the presence of hidden sub-populations. \textit{Statistical Methods $\&$ Applications}.March 2015, Volume 24, Issue 1, pp 97-119. 

\item \textbf{KK Dey}, S Bhattacharya. On Geometric Ergodicity of Additive and Multiplicative Transformation Based Markov Chain Monte Carlo in High Dimensions. \textit{Brazilian Journal of Probability and Statistics}. Accepted. \\
(http://arxiv.org/pdf/1312.0915v2.pdf)

\item S Pradhan, P Patra, S Mitra, \textbf{KK Dey}, S Basu, S Chandra, P Palit, A Goswami. Copper Nanoparticle (CuNP) Nanochain Arrays with a Reduced Toxicity Response: A Biophysical and Biochemical Outlook on Vigna radiata. \textit{J. Agric. Food Chem}, 2015, 63 (10), pp 2606 - 2617.  

\item S Mitra, P Patra, S Pradhan, N Debnath, \textbf{KK Dey}, S Sarkar, D Chattopadhyay, A Goswami. Microwave synthesis of $ZnO@mSiO2$ for detailed antifungal mode of action study: Understanding the insights into oxidative stress. \textit{Journal of Colloid and Interface Science}, Volume 444, 15 April 2015, Pages 97-108. 

\item SR Choudhury, A Basu, \textbf{KK Dey}, T Nag, A Goswami. Toxicological Evaluation of Antimicrobially Potent Sulfur Nanoparticles Against Biochemical, Histopathological, and Behavioral Properties in Mice. \textit{Proceedings of the Zoological Society}. June 2015, Volume 68, Issue 1, pp 64-73. 

%253A10.1007%252Fs12595-014-0098-3.pdf?originUrl=http%3A%2F%2Flink.springer.com%2Farticle%2F10.1007%2Fs12595-014-0098-3&token2=exp=1441244794~acl=%2Fstatic%2Fpdf%2F590%2Fart%25253A10.1007%25252Fs12595-014-0098-3.pdf%3ForiginUrl%3Dhttp%253A%252F%252Flink.springer.com%252Farticle%252F10.1007%252Fs12595-014-0098-3*~hmac=2f7e45a1ba6e27a4ab58e3c9c45e6ae8f08b2710f901f8b21a34bfbd4c5ee268)

\item \textbf{KK Dey}, S Bhattacharya. On Single Variable Transformation Approach to Markov Chain Monte Carlo. \textit{JSM Proceedings}. 2014.  

\item S Pradhan, P Patra, S Mitra, \textbf{KK Dey}, S Jain, S Sarkar, S Roy, P Palit, A Goswami. Manganese Nanoparticles: Impact on Non-nodulated Plant as a Potent Enhancer in Nitrogen Metabolism and Toxicity Study both in Vivo and in Vitro. \textit{J. Agric. Food Chem.}, 2014, 62 (35), pp 8777-8785. 

\item S Pradhan, P Patra, S Das, S Chandra, S Mitra, \textbf{KK Dey}, S Akbar, P Palit, A Goswami. Photochemical Modulation of Biosafe Manganese Nanoparticles on Vigna radiata: A Detailed Molecular, Biochemical, and Biophysical Study.  \textit{Environ. Sci. Technol.}, 2013, 47 (22), pp 13122-13131.

\item SR Choudhury,  \textbf{KK Dey}, S Bera, A Goswami. Colloidal stability and coagulation kinetics study of different sized sulphur nanoparticles. \textit{Journal of Experimental Nanoscience}, 8 (3), 2013. 
}
\end{enumerate}


\end{resume}
\end{document}

